Recovering from population extinction in the Animal Life Cycle Algorithm (ALCA)

### 2022-10-02 paper.tex
Updated Paper
Equation Fix
Updated Reference
First Publication Reference Fixed
Updated Info
Basic proyect info updated.

\titlerunning{Animal Life Cycle Algorithm (ALCA)}
% Use \titlerunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\author{J. C. Felix-Saul, Mario Garcia Valdez}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\institute{J. C. Felix-Saul \at Tijuana Institute of Technology, Tijuana, Mexico, \email{jose.felix201@tectijuana.edu.mx}
\and Mario García Valdez \at Tijuana Institute of Technology, Tijuana, Mexico, \email{mario@tectijuana.edu.mx}}
%
% Use the package "url.sty" to avoid
% problems with special characters
% used in your e-mail or web address
%
\maketitle

@@

        \begin{equation}
            \centering
            \begin{matrix}\includegraphics[width=25mm]{img/eq_golden_ratio.pdf}\end{matrix}
            \label{eq.golden_ratio}
            \end{equation}

@@

\begin{acknowledgement}
    This paper has been supported in part by projects DeepBio (TIN2017--85727--C4--2--P) and TecNM Project 11356.21\@.
\end{acknowledgement}

@@

\bibliographystyle{splncs03_unsrt}
%\bibliographystyle{splncs04}
\bibliography{bib/bibliografia.bib}
%\bibliography{10.1007_978-3-031-08266-5_8-citation.bib}

>>>>

\titlerunning{Animal Life Cycle Algorithm (ALCA)}
% Use \titlerunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\author{J. C. Felix-Saul, Mario Garcia Valdez}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\institute{J. C. Felix-Saul \at TecNM, Tijuana Institute of Technology, Tijuana, Mexico, \email{jose.felix201@tectijuana.edu.mx}
\and Mario García Valdez \at TecNM, Tijuana Institute of Technology, Tijuana, Mexico, \email{mario@tectijuana.edu.mx}}
%
% Use the package "url.sty" to avoid
% problems with special characters
% used in your e-mail or web address
%
\maketitle

@@

        \begin{equation}
            \begin{matrix}\includegraphics[width=25mm]{img/eq_golden_ratio.pdf}\end{matrix}
            \label{eq.golden_ratio}
            \end{equation}

@@

\begin{acknowledgement}
    This paper has been supported in part by TecNM Project 15340.22-P.
\end{acknowledgement}

@@

\bibliographystyle{splncs03_unsrt}
%\bibliographystyle{splncs04}
\bibliography{bib/bibliografia.bib}
